Improving Cell Segmentation and Tracking via Mechanistic Models of Rod-Shaped Bacteria

### 2025-09-15 paper_segmentation_tracking/main.tex
add more authors
write short abstract

\author{
    \href{https://orcid.org/0009-0001-0613-7978}{
        \includegraphics[scale=0.06]{figures/orcid.pdf}
        \hspace{1mm}Jonas Pleyer
    }$^1$
	% \texttt{jonas.pleyer@fdm.uni-freiburg.de} \\
	%% examples of more authors
	\href{https://orcid.org/0000-0002-6371-4495}{
        \includegraphics[scale=0.06]{figures/orcid.pdf}
        \hspace{1mm}Christian Fleck
    }$^1$\\\\
    $^1$Freiburg Center for Data Analysis, Modeling and AI, University of Freiburg\\
}

@@

%###################################################################################################
\begin{abstract}
\end{abstract}

>>>>

\author{
    \href{https://orcid.org/0009-0001-0613-7978}{
        % \includegraphics[scale=0.06]{figures/orcid.pdf}
        \hspace{1mm}Student XYZ
    }$^1$
    \href{https://orcid.org/0009-0001-0613-7978}{
        \includegraphics[scale=0.06]{figures/orcid.pdf}
        \hspace{1mm}Jonas Pleyer
    }$^2$
    \href{https://orcid.org/0009-0001-0613-7978}{
        % \includegraphics[scale=0.06]{figures/orcid.pdf}
        \hspace{1mm}Jelena Bratulić
    }$^1$
	% \texttt{jonas.pleyer@fdm.uni-freiburg.de} \\
	%% examples of more authors
	\href{https://orcid.org/0000-0002-6371-4495}{
        \includegraphics[scale=0.06]{figures/orcid.pdf}
        \hspace{1mm}Christian Fleck
    }$^2$
	\href{https://orcid.org/0000-0002-6371-4495}{
        % \includegraphics[scale=0.06]{figures/orcid.pdf}
        \hspace{1mm}Thomas Brox
    }$^1$\\\\
    $^1$University of Freiburg, Germany\\
    $^2$Freiburg Center for Data Analysis, Modeling and AI\\
}

@@

%###################################################################################################
\begin{abstract}
    The detection of individual cells from microscopic images is common practice with many
    biological studies.
    A variety of deep-learning algorithms are under active development to tackle these tasks.
    This study discusses how the training of such algorithms can be improved by generated synthetic
    data from a parametrized, mechanistic single-cell model.
    We use our recent advancements where we have shown how to estimate the parameters of a
    generalized mechanical model for rod-shaped bacteria to generate cell masks and extend the work
    by generating synthetic, near-realistic microscopic images utilizing known effects such as noise
    and other defects that ocurr naturally within these images.
    Using these methods, we investigate how differing approaches benefit from the additional data
    and how various defects within our microscopic images impact their performances.
\end{abstract}
